### 2025-02-19 paper/paper.tex

\usepackage[
backend=biber,
style=authoryear-comp,
]{biblatex}

@@

\addbibresource{RMbibliography.bib}
\onehalfspacing
\parindent=0pt
\usepackage{pagecolor}
\pagecolor{white}
\begin{document}

@@

\begin{table}[h]
    \centering
    \begin{tabular}{|c|c|c|c|c|}
        \hline
        Methods & Avg MSE of regression coefficients &  $\text{Bias}^2$ & Variance & Dataset: Multicollinearity level \\
        \hline
        OLS & 0.0001 & 0.0 & 0.0001 & \multirow{3}{*}{No multicollinearity} \\
        PCR & 0.0063 & 0.0 & 0.0063 &  \\
        PLS & 0.0001 & 0.0 & 0.0001 &  \\
        \hline
        OLS & 0.6598 & 0.0002 & 0.6596 & \multirow{3}{*}{Moderate} \\        
        PCR & 0.2414 & 0.2334 & 0.0080 &  \\
        PLS & 0.2305 & 0.2285 & 0.0020 &  \\
        \hline
        OLS & 12.7383 & 0.0072 & 12.7310 & \multirow{3}{*}{Severe} \\
        PCR & 0.5993 & 0.4221 & 0.1772 &  \\
        PLS & 0.4118 & 0.2719 & 0.1400 &  \\ 
        \hline
    \end{tabular}
    \caption{MSE coefficient decomposition across different different multicollinearity levels}
    \label{tab:Stability_analysis}
\end{table}

\printbibliography

>>>>

@@

\onehalfspacing
\parindent=0pt
\usepackage{pagecolor}
\pagecolor{white}

\begin{document}

@@

\begin{table}[h]
    \centering
    \begin{tabular}{|c|c|c|c|c|}
        \hline
        Methods & Avg MSE of regression coefficients &  $\text{Bias}^2$ & Variance & Dataset: Multicollinearity level \\
        \hline
        OLS & 0.0001 & 0.0 & 0.0001 & \multirow{3}{*}{No multicollinearity} \\
        PCR & 0.0063 & 0.0 & 0.0063 &  \\
        PLS & 0.0001 & 0.0 & 0.0001 &  \\
        \hline
        OLS & 0.6598 & 0.0002 & 0.6596 & \multirow{3}{*}{Moderate} \\        
        PCR & 0.2414 & 0.2334 & 0.0080 &  \\
        PLS & 0.2305 & 0.2285 & 0.0020 &  \\
        \hline
        OLS & 12.7383 & 0.0072 & 12.7310 & \multirow{3}{*}{Severe} \\
        PCR & 0.5993 & 0.4221 & 0.1772 &  \\
        PLS & 0.4118 & 0.2719 & 0.1400 &  \\ 
        \hline
    \end{tabular}
    \caption{MSE coefficient decomposition across different different multicollinearity levels}
    \label{tab:Stability_analysis}
\end{table}
\newpage

\begin{thebibliography}{99}

\bibitem{Hastie2009}
Hastie, Trevor, Tibshirani, Robert, and Friedman, Jerome. (2009). \textit{The Elements of Statistical Learning: Data Mining, Inference, and Prediction}. Springer. DOI: \href{https://doi.org/10.1007/978-0-387-84858-7}{10.1007/978-0-387-84858-7}

\bibitem{James2021}
James, Gareth, Witten, Daniela, Hastie, Trevor, and Tibshirani, Robert. (2021). \textit{An Introduction to Statistical Learning: with Applications in R}. Springer. DOI: \href{https://doi.org/10.1007/978-1-0716-1418-1}{10.1007/978-1-0716-1418-1}

\bibitem{Brunton2019}
Brunton, Steven L., and Kutz, J. Nathan. (2019). \textit{Data-Driven Science and Engineering: Machine Learning, Dynamical Systems, and Control}. Cambridge University Press. DOI: \href{https://doi.org/10.1017/9781108380690}{10.1017/9781108380690}

\bibitem{Johnstone2009}
Johnstone, Iain M., and Lu, Arthur Yu. (2009). On consistency and sparsity for principal components analysis in high dimensions. \textit{Journal of the American Statistical Association}, 104(486), 682–693. DOI: \href{https://doi.org/10.1198/jasa.2009.0121}{10.1198/jasa.2009.0121}

\bibitem{Greenberg1975}
Greenberg, Edward. (1975). Minimum variance properties of principal component regression. \textit{Journal of the American Statistical Association}, 70(349), 194–197. DOI: \href{https://doi.org/10.1080/01621459.1975.10480287}{10.1080/01621459.1975.10480287}

\bibitem{Agarwal2021}
Agarwal, Anish, Shah, Devavrat, Shen, Dennis, and Song, Dogyoon. (2021). On robustness of principal component regression. \textit{Journal of the American Statistical Association}, 116(536), 1731–1745. DOI: \href{https://doi.org/10.1080/01621459.2021.1928513}{10.1080/01621459.2021.1928513}

\bibitem{Rosipal2006}
Rosipal, Roman, and Krämer, Nicole. (2006). Overview and recent advances in partial least squares. In Saunders, Craig, Grobelnik, Marko, Gunn, Steve, and Shawe-Taylor, John (Eds.), \textit{Subspace, Latent Structure and Feature Selection} (pp. 34–51). Springer, Berlin, Heidelberg. DOI: \href{https://doi.org/10.1007/11752790_2}{10.1007/11752790\_2}

\bibitem{Garthwaite1994}
Garthwaite, Paul H. (1994). An interpretation of partial least squares. \textit{Journal of the American Statistical Association}, 89(425), 122–127. DOI: \href{https://doi.org/10.1080/01621459.1994.10476452}{10.1080/01621459.1994.10476452}

\bibitem{Goktas2020}
Göktaş, Atila, and Akkuş, Özge. (2020). Comparison of partial least squares with other prediction methods via generated data. \textit{Journal of Statistical Computation and Simulation}, 90(16), 3009–3024. DOI: \href{https://doi.org/10.1080/00949655.2020.1793342}{10.1080/00949655.2020.1793342}

\bibitem{Vinzi2013}
Esposito Vinzi, Vincenzo, and Russolillo, Giorgio. (2013). Partial least squares algorithms and methods. \textit{WIREs Computational Statistics}, 5(1), 1–19. DOI: \href{https://doi.org/10.1002/wics.1239}{10.1002/wics.1239}

\bibitem{deJong1993}
de Jong, Sijmen. (1993). SIMPLS: An alternative approach to partial least squares regression. \textit{Chemometrics and Intelligent Laboratory Systems}, 18(3), 251–263. DOI: \href{https://doi.org/10.1016/0169-7439(93)85002-X}{10.1016/0169-7439(93)85002-X}

\bibitem{Lin2016}
Lin, You-Wu, Deng, Bai-Chuan, Xu, Qing-Song, Yun, Yong-Huan, and Liang, Yi-Zeng. (2016). The equivalence of partial least squares and principal component regression in the sufficient dimension reduction framework. \textit{Chemometrics and Intelligent Laboratory Systems}, 150, 58–64. DOI: \href{https://doi.org/10.1016/j.chemolab.2015.11.003}{10.1016/j.chemolab.2015.11.003}

\end{thebibliography}
